Can We Crunch the Social Graph on the Cheap?

### 2011-01-25 doc/hotpar2011/softxmt-hotpar2011.tex
evaluation, post-meeting pass

\section{Related work}
\label{sec:related}
The concept of using independent parallel contexts to tolerate latency
is not novel.  The inspiration for our project is of course the Cray
XMT \cite{feo-xmt}, which implemented a hardware version of our
programming model (in what would today be considered exceptionally
slow silicon.)  The XMT can be seen as simultaneous multithreading
\cite{tullsen-smt} writ large; the technique and motivation is
essentially the same, but the XMT allows hundreds of contexts (modern
Intel SMT implementations are generally limited to two.) The Alewife
system \cite{agarwal-alewife} also switches contexts (in hardware) to
hide latency on remote-node accesses.  Cyclops \cite{almasi-cyclops}
allows hundreds of independently executing contexts to share FPUs,
caches, and paths to memory, but does not context switch or share
basic execution hardware.

Modern programmable GPUs, such as nVidia's CUDA programming model, can also be interpreted in using an XMT-like
model under the hood;
% Do I need to include a citation here?
while they generate large numbers of available execution contexts via
a (semi-)explicit SIMD model, those SIMD instructions keep functional
units satisfied by overlapping execution with the loads required for
other contexts.

Similar techniques have also been used in software.  Mowry proposed a system \cite{mowry-scm} of \emph{software-controlled
  multithreading}.  As opposed to our system of explicitly marked
remote references, SCM assumes a high hit rate and traps to an
interrupt routine which performed a context switch upon a cache miss.  The 2000-era processors had
short enough latencies that using more than two contexts generally
produced slowdown.

Partitioned global address space models, such as that used in Unified Parallel C,
% definitely need a citation here
 share our approach of exposing all data (even remote data)
 transparently to any threads and have largely solved the problems of
 how to efficiently translate those remote reads into message
 passing.  However, their programming models emphasize locality more
 than our work does; while a program can examine any vertex in a UPC
 program at any time, it probably shouldn't (whereas our kernels rely on our
 latency hiding technique to make common remote references fast.

The value of the information in extremely large and sparse graphs is
rapidly growing.  The GraphCT toolkit \cite{ediger-graphct} used an XMT to perform
sophisticated analysis on data from Twitter, identifying important
actors and their networks of influence, and it can scale to the full
size of graphs such as Facebook's friend network.
\section{Programming model}
\label{sec:model}

Our shared-memory programming model partitions the overall address
space into a global shared address space and per node private address
spaces.  Locality may be exploited directly by the programmer in the
node private address spaces, just as in a conventional cache-coherent
multiprocessor node.  In contrast, the global space is explicitly
uncached.  There, every processor can access any word of memory
directly via its unique global address.

Whereas in the PGAS model coherency of global copies is implictly
maintained across the system, we forego caching of globally shared
data.  A node can exploit temporal locality of data stored in
the global space only by first copying it into the node's local space.
In this way, a node can access data at random across the system while
incurring no hardware coherence overhead: consistency is enforced by
our mechanisms for explicit global synchronization.

The model promises efficiency subject to the presence of sufficient
concurrency.  Exactly how that concurrency is expressed by the
programmer is language dependent.  Our programming model serves to
augment threaded programming languages so that they become latency
tolerant on large address spaces.  Software multithreading is used to
provide latency tolerance: a computation that is about to execute a
long latency operation such as a remote memory reference initiates the
operation and then yields to the scheduler, which quickly resumes
execution of another computation.  Concurrency is also used -- via
aggregation of requests to a common node destination -- to make more
efficient use of network bandwidth and in some cases reduce bandwidth
demands.

Synchronization on locations in the node private address space is the
same as on conventional systems.  Synchronization on global addresses
works differently: we provide atomic operations such as {\tt
  int\_fetch\_add} as well as operations using full-bits, as on the
Cray XMT.  As is true for other long latency operations,
synchronization latency is tolerated by yielding to the scheduler.
Even non-blocking global atomics yield: atomic operations executed as
x86 instructions sabbotage concurrency by forcing all outstanding
memory references to complete before new ones can be issued.  By
yielding, the core can switch to another computation while the
synchronization is accomplished outside of the pipeline.  In addition,
the implementation can exploit aggregation when concurrency is
abundant to increase the throughput of global synchronization.

Thus, the programming model provides the programmer with options: express
locality within the private space, and it will be exploited to reduce
latency and bandwidth; express concurrency, and it will be used toward
tolerating latency and reducing the cost of bandwidth.

\begin {comment}
\todo{Change to discuss API:

@@

We would like to run as fast as current hardware will let us. Pin
bandwidth is the tightest resource: Intel's QuickPath Interconnect
(QPI) allows approximately 100 million requests per second
\cite{quickpath:website} \todo{specifically 25.6GB/s two way, which we expect 6.4GB/s for one way for outgoing request}, and recent interconnect products allow similar request
rates, with a round-trip latency of approximately 3$\mu$s
\todo{cite}. Little's law tells us then that we must support on the
order of 300 concurrent memory operations--and thus, up to this many coroutines--to
cover this latency.

@@

But we have to be careful---directing memory requests from multiple
compute threads to a single memory manager thread may reduce memory
concurrency. And we have increased the overhead of a single memory
operation: what in the single node case was a simple read, is now
multiple queuing operations between threads and multiple reads and
writes over QPI to the network interface. Adding more memory manager
threads may enable more memory concurrency, but the overhead is still high \todo{why? because lots of code to run? so accel by impl in hardware. Maybe this is answered by the "what in...is now" already}

\subsubsection{Hardware management}
\todo{might want to call it accelerator throughout after saying FPGA once}
Considering this overhead, we propose hardware acceleration with a {\em memory manager
  FPGA}, a coprocessor FPGA inserted into a Xeon socket so it can
participate in the node's coherence domain. This coprocessor does no
computation---it would only manage the global memory requests of the
main CPU, performing the function of the memory manager thread
described earlier.

@@

To evaluate the feasibility of our proposal, we ran pointer chasing
benchmarks on a single-node implementation of our runtime. These
pointer chasing experiments are intended to model a particular
``wost-case'' behavior of irregular applications, where each memory
reference causes a cache miss.

We ran these experiments on a Dell PowerEdge R410 with two Xeon X5650
processors and 24GB of RAM, with hyperthreading disabled. These
processors use a NUMA memory architecture, where each processor has
its own integrated memory controller and DIMMs; references to other
processors are carried over Intel's cache-coherent QuickPath
Interconnect (QPI).

Our evaulation consists of three parts. First, we describe the
performance of the test machine's memory system to use as a
baseline. Then, we demonstrate that the same performance is achievable
using our runtime system: we measure pointer chasing performance and
the effects of cache pressure due to the number of contexts
required. Finally, we simulate the effects of fetching memory over a
network by adding delays to our runtime.

\subsection{Memory system performance}

We first characterize the performance of our test machine's memory
system. We measured three parameters: the maximum random reference
rate that can be issued by the cores in one processor, the maximum random
reference rate that can be serviced by one processor's memory controller,
and the maximum random reference rate that can be carried over the QPI
link and serviced by another processor's memory controller.

To find the maximum random reference rate that one processor's cores
can issue, we ran pointer chasing code following the model of
Figure~\ref{fig:pointernocoro}. Each core issues $n$ list traversals
in a loop; we call $n * \textit{number of cores}$ the number of
{\em concurrent offered references}, since the memory system may not
be able to satisfy them all in parallel. Since our goal is to find a
baseline for evaluating our coroutine library, we depend on the
processor's ILP for memory concurrency, rather than our coroutine
library.

\begin{figure}
\begin{alltt}
  while (count-- > 0) \{
    list1 = list1->next;
    list2 = list2->next;
    \ldots
    list\(n\) = list\(n\)->next;
  \}
\end{alltt}
\caption{Pseudocode for pointer chasing without coroutines.}
\label{fig:pointernocoro}
\end{figure}

@@

Figure~\ref{fig:listwalk-totalconc} shows the result. Each point represents
the maximum rate pointers are traversed for a given number of
concurrent offered references. We see a maximum rate of 277 million
references per second, which agrees with the measurements found by \cite{Mandal:2010} with a similar machine. This rate is achieved when the number of offered
references is 42 \todo{yes, max is achieved here but essentially levels out earlier like 36; do we want a percentage metric for defining a plateau}. Note that a single core cannot support this level of
memory concurrency; the maximum reference rate for a single core is
107M. We believe this limit is due to the core's {\em line fill
  buffer} \todo{cite nehalem perf docs}, which limits the core to 10
concurrent L2 misses.

The memory controller in the processor has more bandwidth than its
cores can saturate. To measure the memory controller's maximum random
reference rate, we extended the previous experiment so that cores in
both processors were traversing lists allocated in the first processor's
memory. With this configuration, we observed a maximum rate of 360
million references per second. We believe this difference is due to
the configuration of the processor's {\em Global Queue} \todo{cite nehalem
  docs}, which limits the number of concurrently-executing read misses
from a processor's cores to its local last-level cache and memory to 32.

% take this figure out if we need the space
% the main point is room for remote references to local memory
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/qpi_bw-edited.pdf}
  \end{center}
  \caption{Pointer chasing in a remote processor's memory.}
  \label{fig:listwalk-qpi}
\end{figure}

Finally, we measured the rate at which the cores can make requests
over the QPI link. For this experiment, we allocated the lists in the
second processor, and ran the traversals on the first
processor. Figure~\ref{fig:listwalk-qpi} shows the result. We found that use
of the QPI link limits us to 175 million references per second.

\subsection{Runtime performance}

To characterize the performance of our runtime, we investigated three
effects: the maximum reference rate using coroutines
to obtain memory concurrency, the effects of cache pressure from the
coroutines' context storage, and the maximum reference rate obtainable
using a simulated network delay.

\begin{figure}
\begin{alltt}
  while (count-- > 0) \{
     prefetch(&(list1->next));
     prefetch(&(list2->next));
     \ldots
     prefetch(&(list\(n\)->next));
     switch();
     list1 = read(&(list1->next));
     list2 = read(&(list2->next));
     \ldots
     list\(n\) = read(&(list\(n\)->next));
 \}
\end{alltt}
\caption{Pseudocode for pointer chasing using coroutines.}
\label{fig:pointercoro}
\end{figure}

To find the maximum reference rate obtainable using our coroutine
library, we modified our pointer chasing benchmark as shown in
figure~\ref{fig:pointercoro}. Now there are two sources of offered
concurrent references: the ILP exploited by the processor, and the
memory concurrency enabled by prefetching and switching to a new
coroutine. As with our first experiment, we allocated the lists in the
same processor as the cores doing the traversal.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/multi-green-edited.pdf}
  \end{center}
  \caption{Pointer chasing with coroutines, with one reference per
    coroutine.}
  \label{fig:multi-green}
\end{figure}

Figure~\ref{fig:multi-green} shows the result. For this
experiment, we limited memory concurrency to one concurrent miss per
coroutine, so the only source of memory concurrency is the use of
coroutines. We are able to obtain a rate of 275 million references per
second with 48 concurrent misses, or 8 coroutines per core. These
results are very close to the ILP-only experiment.

We observe a gradual decrease in reference rate once the number of
concurrent references per core exceeds 10; we believe this is due to
later prefetches squashing earlier ones in the line fill buffer. We
also observe some repeatable outliers below the maximum rate even with enough
memory concurrency; this is harder to explain, but we suspect it is
due to resource contention in the cores' pipelines once the memory
system is full of requests.

\begin{figure}
\begin{alltt}
  while (count-- > 0) \{
    prefetch(&(list1->next));
    switch();
    list1 = read(&(list1->next));
    for( i in 1 to num_local_updates ) \{
      local->data++;
      local = local->next;
   \}
  \}
\end{alltt}
\caption{Pseudocode for pointer chasing with local updates.}
\label{pointerupdate}
\end{figure}

The stacks for the coroutines are stored in the data cache, where they
will compete for space with an application's data. To characterize the
effects of this cache pressure, we modified our list chasing benchmark
to include random updates to a per-coroutine local data structure that
is small enough to fit in cache. Figure~\ref{pointerupdate} shows the
general idea.

@@

Finally, to simulate the performance of pointer chasing in a
multi-node system, we modified the scheduler of our coroutine library
to include a delay before a coroutine can be rescheduled, imitating
the network transit delay even though we are referencing local
memory. Recently published measurements of Infiniband latencies
\todo{cite} suggest we might expect 1.1 $\mu$s source-to-destination
latencies between two computers connected back-to-back; we assume a
switch transit delay of 400 ns in each direction and thus estimate a 3
$\mu$s round-trip delay. In this experiment, once a coroutine has
yielded, we use the core's timestamp counter to ensure it does not get
rescheduled for 3 $\mu$s.

@@

We ran these experiments with two sources of memory concurrency: each
core ran up to 167 coroutines, and each coroutine made between 1 and 4
concurrent references. The results are shown in
Figure~\ref{fig:network-delay}. We are still able to reach a
near-maximum rate of 273 million references per second, but at least 3
concurrent references per coroutine are required. Running with a single
reference per coroutine achieves 236 million references per
second. Any network interface would be connected through a QPI link,
which we measured to have a bandwidth limit of 175 million references
per second, so our runtime appears to have the capacity to chase pointers
in a remote memory.

\todo{do we want to include that the memory system imposes max limit so really more throughput is still achievable if there are enough ILP memory concurrency?}
\todo{may want to rerun with memory on remote core to incorporate QPI limit?}

>>>>

\section{Related work}
\label{sec:related}

\todo{actually write this}

Multithreading for latency tolerance has been explored in a number of directions.

Hardware approaches: The Tera MTA and Cray XMT, the MIT Alewife
project, ??? use hardware context switches to tolerate memory latency
for large systems. More recently, Simultaneous Multi-Threading,
Niagara, Cyclops, and even GPUs switch between multiple contexts to
tolerate memory latency, for memory that is hundreds of cycles of
away, rather than the thousands we must tolerate.

software:

Mowry's SCM

Cullers' TAM

qthreads

cilk? tbb?

why not wait for more cores?

\section{Programming model}
\label{sec:model}

\todo{Change to discuss API:

@@

We would like to run as fast as current hardware will let us. Pin
bandwidth is the tightest resource: Intel's QuickPath Interconnect
(QPI) allows approximately 100 million requests per second
\cite{quickpath:website} \todo{specifically 25.6GB/s two way, which we expect 6.4GB/s for one way for outgoing request}, and recent interconnect products allow similar request
rates, with a round-trip latency of approximately 3$\mu$s
\todo{cite} \todo{we calculate the 3us in the evaluation based on some numbers for sw-to-sw plus switches, should we pull that up here?}. Little's law tells us then that we must support on the
order of 300 concurrent memory operations--and thus, up to this many coroutines--to
cover this latency.

@@

But we have to be careful---directing memory requests from multiple
compute threads to a single memory manager thread may reduce memory
concurrency. And we have increased the overhead of a single memory
operation: what in the single node case was a simple read, is now
multiple queuing operations between threads and multiple reads and
writes over QPI to the network interface. Adding more memory manager
threads may enable more memory concurrency, but the overhead is still high \todo{reword so overhead still high sounds supported as above}
\subsubsection{Hardware management}
\todo{might want to call it accelerator throughout after saying FPGA once}
Considering this overhead, we propose hardware acceleration with a {\em memory manager
  FPGA}, a coprocessor FPGA inserted into a Xeon socket so it can
participate in the node's coherence domain. This coprocessor does no
computation---it would only manage the global memory requests of the
main CPU, performing the function of the memory manager thread
described earlier.

@@

Our goal is to evaluate the feasibility of our proposed runtime. We want to determine two things: whether coroutines can generate memory concurrency without incurring minimal performance overhead, and whether the system can support the level of concurrency required to tolerate the latency that will be present in a multi-node system.

We focus the evaluation on one component of the runtime: lightweight context switching. We ran pointer-chasing benchmarks on a single-node implementation of our runtime. These pointer chasing experiments are intended to model a particular ``worst-case'' behavior of irregular applications, where each memory reference causes a cache miss.

We ran these experiments on a Dell PowerEdge R410 with two Xeon X5650 (Nehalem microarchitecture)
chips and 24GB of RAM, with hyperthreading disabled. These
chips use a NUMA memory architecture, where each chip has
its own integrated memory controller and DIMMs; references to other
chips' memory are carried over Intel's cache-coherent QuickPath
Interconnect (QPI).

Our evaulation consists of two parts. First, we demonstrate that the runtime system can achieve the same performance as when there is explicit memory concurrency available: we measure pointer chasing performance and
the effects of cache pressure due to the number of contexts required. Second, we look at the runtime within the multi-node picture and simulate the effects of fetching memory over a network to show that the runtime can reach the level of concurrency required to hide the latency. In each part we begin by studying relevant aspects of our test machine's memory system so we can interpret our runtime results.

\subsection{Single-node}

We first characterize the performance of our test machine's memory
system. Then we use these results to evaluate the performance of our runtime within a single node.

\subsubsection{Base memory system performance}
\todo{title might be improved}

We measured two parameters: the maximum random reference
rate that can be issued by the cores in one chip and the maximum random
reference rate that can be serviced by one chip's memory controller.\todo{The 360M  "serviced" number could perhaps be an "aside" kind of paragraph since not supporting a major point}

To find the maximum random reference rate that one chip's cores
can issue, we ran pointer chasing code following the model of
Figure~\ref{fig:code}a. Each core issues $n$ list traversals
in a loop; we call $n * \textit{number of cores}$ the number of
{\em concurrent offered references}, since the memory system may not
be able to satisfy them all in parallel. Since our goal is to find a
baseline for evaluating our coroutine library, we depend on the
cores' exploitation of ILP for memory concurrency, rather than our coroutine
library.

\begin{figure*}[ht]
%list walk ILP
\begin{minipage}[b]{0.3\linewidth}
\centering
\begin{alltt}
  while (count-- > 0) \{
    list1 = list1->next;
    list2 = list2->next;
    \ldots
    list\(n\) = list\(n\)->next;
  \}
  \center{{\bf (a)}}
\end{alltt}
%\caption{Pseudocode for pointer chasing without coroutines.}
\label{fig:pointernocoro}
\end{minipage}
%listwalk green threads
\begin{minipage}[b]{0.35\linewidth}
\centering
\begin{alltt}
  while (count-- > 0) \{
     prefetch(&(list1->next));
     switch();
     list1 = read(&(list1->next));
 \}
  \center{{\bf (b)}}
\end{alltt}
  %%n lists
  % while (count-- > 0) \{
  % prefetch(&(list1->next));
  %   prefetch(&(list2->next));
   %  \ldots
   %  prefetch(&(list\(n\)->next));
   %  switch();
   %  list1 = read(&(list1->next));
   %  list2 = read(&(list2->next));
   %  \ldots
   %  list\(n\) = read(&(list\(n\)->next));
%\caption{Pseudocode for pointer chasing using coroutines.}
\label{fig:pointercoro}
\end{minipage}
%cache pressure
\begin{minipage}[b]{0.32\linewidth}
\centering
\begin{alltt}
  while (count-- > 0) \{
    prefetch(&(list1->next));
    switch();
    list1 = read(&(list1->next));
    for( i in 1 to num_local_updates ) \{
      local->data++;
      local = local->next;
   \}
  \}
   \center{{\bf (c)}}
\end{alltt}
%\caption{Pseudocode for pointer chasing with local updates.}
\label{fig:pointerupdate}
\end{minipage}
\caption{Pseudocode for: (a) pointer chasing without coroutines, (b) pointer chasing using coroutines, (c) pointer chasing with local updates.}
\label{fig:code}
\end{figure*}

@@

Figure~\ref{fig:listwalk-totalconc} shows the result. Each point represents
the maximum rate pointers are traversed for a given number of
concurrent offered references. We see a maximum rate of 277 million
references per second, which agrees with the measurements found by \cite{Mandal:2010} with a similar machine. This rate is achieved when the number of offered references is 36. Note that a single core cannot support this level of
memory concurrency; the maximum reference rate for a single core is
107M. We believe this limit is due to the core's limited number of {\em line fill
  buffers} \cite{nehalem:arch}, which limits the core to 10
concurrent private cache misses.

The memory controller in the chip has more bandwidth than its
cores can saturate. To measure the memory controller's maximum random
reference rate, we extended the previous experiment so that cores in
both processors were traversing lists allocated in the first processor's
memory. With this configuration, we observed a maximum rate of 360
million references per second. We believe this difference is due to
the configuration of the processor's {\em Global Queue} \cite{nehalem:perf}, which limits the number of concurrently-executing read misses from a chips cores to its local last-level cache and memory to 32.

\subsubsection{Runtime performance}

To evaluate the performance of our runtime, we investigated two
effects: the maximum reference rate using coroutines
to obtain memory concurrency and the effects of cache pressure from the
coroutines' context storage.

To find the maximum reference rate obtainable using our coroutine
library, we modified our pointer chasing benchmark as shown in
figure~\ref{fig:code}b. Now there are two sources of offered
concurrent references: the ILP exploited by the processor, and the
memory concurrency enabled by prefetching and switching to a new
coroutine. As with our first experiment, we allocated the lists in the
same processor as the cores doing the traversal.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/multi-green-edited.pdf}
  \end{center}
  \caption{Pointer chasing with coroutines, with one reference per
    coroutine. Number of coroutines per core is $\textit{total concurrent references} / \textit{number of cores}$.}
  \label{fig:multi-green}
\end{figure}

Figure~\ref{fig:multi-green} shows the result. For this
experiment, we limited memory concurrency to one concurrent miss per
coroutine, so the only source of memory concurrency is the use of
coroutines. We are able to obtain a rate of 275 million references per
second with 48 concurrent misses, or 8 coroutines per core. These
results are very close to the ILP-only experiment, but more concurrent requests are required--about 48 versus 36. When the number of references per coroutine is larger than 1, fewer coroutines are required to reach full performance.

We observe a gradual decrease in reference rate once the number of
concurrent references per core exceeds 10; we believe this is due to
later prefetches squashing earlier ones in the line fill buffers. We
also observe some points that do not follow the trend and look like noise, but these results are actually repeatable. This effect is harder to explain, but we suspect it is
due to resource contention in the cores' pipelines once the memory
system is full of requests.

%Such points are repeatably lower, and looks like the std dev of such points (the diamond ones than are low) is also higher than other "normal" points: around 35M versus 13M or less, which seems to suggest a weird effect at those numbers}

The stacks for the coroutines are stored in the data cache, where they
will compete for space with an application's data. To characterize the
effects of this cache pressure, we modified our list chasing benchmark
to include random updates to a per-coroutine local data structure that
is small enough to fit in cache. Figure~\ref{fig:code}c shows the
general idea.

@@

\subsection{Multi-node}

To evaluate the potential for our runtime to perform in the multi-node case, we simulated a network delay and saw whether the runtime could tolerate the larger latency. First we measure the QPI bandwidth between the two chips of the test machine, since the chip would talk to the network interface over a QPI link.

% take this figure out if we need the space
% the main point is room for remote references to local memory
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/qpi_bw-edited.pdf}
  \end{center}
  \caption{Pointer chasing in a remote processor's memory.}
  \label{fig:listwalk-qpi}
\end{figure}
%%%%%%%%%%

We measured the rate at which the cores can make requests
over the QPI link. For this experiment, we allocated the lists in the
second chip's memory and ran the traversals on the first chip's cores. Figure~\ref{fig:listwalk-qpi} shows the result. We found that use of the QPI link limits us to 175 million references per second.

To simulate the performance of pointer chasing in a
multi-node system, we modified the scheduler of our coroutine library
to include a delay before a coroutine can be rescheduled, imitating
the network transit delay even though we are referencing local
memory. Recently published measurements of Infiniband latencies
\todo{cite} suggest we might expect 1.1 $\mu$s source-to-destination
latencies between two computers connected back-to-back; we assume a
switch transit delay of 400 ns \todo{how many hops} in each direction and thus estimate a 3
$\mu$s round-trip delay. In this experiment, once a coroutine has
yielded, we use the core's timestamp counter to ensure it does not get
rescheduled for 3 $\mu$s.

@@

We ran these experiments with two sources of memory concurrency: each
core ran up to 167 coroutines, and each coroutine made between 1 and 4
concurrent references. The results are shown in
Figure~\ref{fig:network-delay}. We are still able to reach a
near-maximum rate of 273 million references per second, but at least 2
concurrent references per coroutine are required. Running with a single
reference per coroutine achieves 236 million references per
second. Any network interface would be connected through a QPI link,
which we measured to have a bandwidth limit of 175 million references
per second, so our runtime appears to have the capacity to chase pointers
in a remote memory.

\todo{do we want to include that the memory system imposes max limit so really more throughput is still achievable if there are enough ILP memory concurrency?}\\
\todo{also have results that remote cores over QPI plus delay 3us can make it up to the 175M, with sufficient number of coroutines}
